\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}

### 2023-03-24 paper/short/main_wc995.tex
Update paper

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016},
a third of whom experience functional cognitive impairment and diminished quality of life
\cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds
in a habituation therapy term \textit{sound therapy},
or as part of cognitive behavioral therapy \cite{tunkelClinicalPracticeGuideline2014}.
Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015}.
However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about $50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.

@@

Two spectrally complex and complementary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (Fig. \ref{fig:spectra}).

@@

Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$). $X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig. \ref{fig:experimentdiagram}).
Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
Presentation level (in dB sound pressure level (SPL)) was not recorded.
Procedures were approved by the UMass IRB.

>>>>

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016},
a third of whom experience functional cognitive impairment and diminished quality of life
\cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds
in a habituation therapy termed \textit{sound therapy},
or as part of cognitive behavioral therapy \cite{tunkelClinicalPracticeGuideline2014}.
Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,schoisswohlAmplitudeModulatedNoise2019}.
However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about 50-80\% of patients \cite{neffComparingThreeEstablished2019,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
There is a need for methods to characterize the remaining 20-50\% of nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.

@@

Two spectrally complex and complementary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (power-spectral densities are displayed in the botton subplots of Fig. \ref{fig:spectra}).

@@

Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$). $X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig. \ref{fig:experimentdiagram}).
Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
Presentation level (in dB SPL) was not recorded.
Procedures were approved by the UMass IRB.
